### 2024-05-18 fantasy-football.qmd
20240518 - define abbreviations

Note: "PAT" = point after touchdown; "FG" = field goal

@@

- "TD" = touchdown
- "INT" = interception
- "yds" = yards
- "ATT" = attempts
- "2 pt conversion" = two-point conversion
- "FG"
- "PAT" = point after touchdown (i.e., extra point/point after attempt)

>>>>

Note: "TD" = touchdown; "PAT" = point after touchdown; "FG" = field goal

@@

- "TD" = touchdown
- "INT" = interception
- "yds" = yards
- "ATT" = attempts
- "2 pt conversion" = two-point conversion
- "FG" = field goal
- "PAT" = point after touchdown (i.e., extra point/point after attempt)
